Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-26 paper/virtual_cytoplasm_v2.tex
tex revised

\caption{A) Solvent accessible surface area (sasa) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). \st{The average sasa for each protein in single molecule simulation is over number of chains of proteins and three replica. The average sasa for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica.} The average bar value for single molecule simulations shows the sum over sasa of each protein chains averaged over the number of replica minus the sasa of the whole proein averaged over the number of replica. The average bar value for cytoplasm simulation shows the sum over sasa of each protein chains averaged over the number of replica and the abundancy of the protein minus the sasa of the whole proein averaged over the number of replica and the abundancy of the protein. The error bars show the standard errors. B) Root mean squared displacement (rmsd) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average rmsd for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}
\label{fig:structural_integrity_chain}
\end{figure}

>>>>

\caption{A) Interface area for oligomers from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). \st{The average sasa for each protein in single molecule simulation is over number of chains of proteins and three replica. The average sasa for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica.} The average bar value for single molecule simulations shows the sum over sasa of each protein chains averaged over the number of replica minus the sasa of the whole protein averaged over the number of replica. The average bar value for cytoplasm simulation shows the sum over sasa of each protein chains averaged over the number of replica and the abundancy of the protein minus the sasa of the whole protein averaged over the number of replica and the abundancy of the protein. The error bars show the standard errors. B) Root mean squared displacement (rmsd) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average rmsd for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}
\label{fig:structural_integrity_chain}
\end{figure}
